Analysis of Bauer et al. (unpublished) Field experiment: <br> Persistence

### 2022-12-14 R/model_persistence_check.Rmd
Update model_persistence_check.Rmd

```{r load-data}
sites <- read_csv(
  here("data", "processed", "data_processed_sites_temporal.csv"),
  col_names = TRUE, na = c("na", "NA", ""),
  col_types = cols(
    .default = "?",
    plot = "f",
    site = "f",
    sand_ratio = "f",
    substrate_depth = col_factor(levels = c("30", "15")),
    target_type = col_factor(levels = c("hay_meadow", "dry_grassland")),
    seed_density = "f",
    exposition = col_factor(levels = c("north", "south")),
    survey_year = "c"
  )
  ) %>%
  ### Exclude data of seed mixtures
  filter(presabu == "presence") %>%
  mutate(
    survey_year_fct = factor(survey_year),
    botanist_year = str_c(survey_year, botanist, exposition, sep = " "),
    botanist_year = factor(botanist_year),
    id = factor(id),
    n = persistence / 100
  ) %>%
  select(
    id, plot, site, exposition, sand_ratio, substrate_depth, target_type,
    seed_density, survey_year_fct, survey_year, botanist_year, n
  )
```

>>>>

```{r load-data}
sites <- read_csv(
  here("data", "processed", "data_processed_sites_temporal.csv"),
  col_names = TRUE, na = c("na", "NA", ""),
  col_types = cols(
    .default = "?",
    plot = "f",
    site = "f",
    sand_ratio = "f",
    substrate_depth = col_factor(levels = c("30", "15")),
    target_type = col_factor(levels = c("hay_meadow", "dry_grassland")),
    seed_density = "f",
    exposition = col_factor(levels = c("north", "south")),
    survey_year = "c"
  )
  ) %>%
  ### Exclude data of seed mixtures
  filter(presabu == "presence") %>%
  mutate(
    survey_year_fct = factor(survey_year),
    botanist_year = str_c(survey_year, botanist, exposition, sep = " "),
    botanist_year = factor(botanist_year),
    id = factor(id),
    n = persistence / 100
  ) %>%
  select(
    id, plot, site, exposition, sand_ratio, substrate_depth, target_type,
    seed_density, survey_year_fct, survey_year, botanist_year, n
  )
sites
```
